Learning the local coding scheme: Jointly Optimized Locally Linear Classifiers

### 2017-09-11 paper/llncs2e/PKDD2017.tex
add pic

			phishing              & Train loss & Test loss & Acc(\%) &test time \\

@@

			Magic04              & Train loss & Test loss & Acc(\%) &test time \\

@@

			IJCNN              & Train loss & Test loss & Acc(\%) &test time\\

@@

			w8a              & Train loss & Test loss & Acc(\%) &test time\\

@@

			\textbf{LLC-JO}         &0.0250$\pm$0.0003  &0.0262$\pm$0.0004  & 98.74 $\pm$ 0.07  &$\times$9.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0213$\pm$0.0016}  &\textbf{0.0228$\pm$0.0028}  &\textbf{98.96 $\pm$ 0.31}   &$\times$9.92\\ \hline

@@

			connect-4              & Train loss & Test loss & Acc(\%) &test time\\

@@

			Covtype              & Train loss & Test loss & Acc(\%) &test time\\

@@

			\textbf{SVM} 		   	&0.0409$\pm$0.0001  &0.0415$\pm$0.0000  &98.15 $\pm$ 0.02  &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.0319$\pm$0.0002  &0.0275$\pm$0.0004  &98.82 $\pm$ 0.04  &$\times$7.08 \\ \hline
			\textbf{LLC-SAPL}       &0.0268$\pm$0.0002  &0.0201$\pm$0.0003  &99.03 $\pm$ 0.03 &$\times$7.17  \\ \hline
			\textbf{LLC-JO}         &\textbf{0.0258$\pm$0.0007}  &\textbf{0.0194$\pm$0.0008}  &\textbf{99.08 $\pm$ 0.02}  &$\times$7.28 \\ \hline

>>>>

			phishing              & Train loss & Test loss & Acc(\%) &Test time \\

@@

			Magic04              & Train loss & Test loss & Acc(\%) &Test time \\

@@

			IJCNN              & Train loss & Test loss & Acc(\%) &Test time\\

@@

			w8a              & Train loss & Test loss & Acc(\%) &Test time\\

@@

			\textbf{LLC-JO}         &0.0250$\pm$0.0003  &0.0262$\pm$0.0004  & 98.74 $\pm$ 0.07  &$\times$10.01\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.0213$\pm$0.0016}  &\textbf{0.0228$\pm$0.0028}  &\textbf{98.96 $\pm$ 0.31}   &$\times$10.28\\ \hline

@@

			connect-4              & Train loss & Test loss & Acc(\%) &Test time\\

@@

			Covtype              & Train loss & Test loss & Acc(\%) &Test time\\

@@

			\textbf{SVM} 		   	&0.6536$\pm$0.0005  &0.6535$\pm$0.0007  &68.73 $\pm$ 0.06  &$\times$1 \\ \hline
			\textbf{LLSVM}     		&0.4828$\pm$0.0017  &0.4809$\pm$0.0024  &79.17 $\pm$ 0.04  &$\times$15.18 \\ \hline
			\textbf{LLC-SAPL}       &0.4378$\pm$0.0012  &0.4359$\pm$0.0013  &80.61 $\pm$ 0.10 &$\times$16.72  \\ \hline
			\textbf{LLC-JO}         &0.4122$\pm$0.0025  &0.4190$\pm$0.0031  & 81.75 $\pm$ 0.11  &$\times$14.30\\ \hline
			\textbf{LLC-DJO}         &\textbf{0.4045$\pm$0.0037}  &\textbf{0.4095$\pm$0.0040}  &\textbf{81.99 $\pm$ 0.21}   &$\times$14.52\\ \hline
